---
title: "Galton Family : Shiny Application and Reproducible Pitch"
Author : "Joe Okelly"
date : "08/30/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## GaltonFamilies Analysis Report

Galton Families Analysis Report enabled developing data products using shiny apps 
Embedded using RMarkDown.

Use the Pageup and Pagedown keys to travere between slides.

## Application Overview

- Galton Families data set use to predict the childrens height, both son and daughter
- on the basis of the parents height

## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://joejokelly.shinyapps.io/backup/


Click the link below for compiled project files on gitub repo.

https://github.com/Joejokelly/GaltonFamiies-ShinyProject

## Data Used

The data used for this application is diamonds data set, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.

```{r, echo=FALSE}
library(shiny)
library(HistData)
data("GaltonFamilies")
library(dplyr)
library(ggplot2)
library("ggplot2")

gf <- GaltonFamilies
head(gf)
```

